Stream Mining Algorithms for Sensor Data Classification

### 2015-05-31 latex/paper-draft.tex

		\begin{abstract}
			%\boldmath
			Learning from data streams is a research area of increasing importance \cite{evaluation_stream_mining}. Nowadays, several stream mining algorithms have been developed. Most of them learn decision tree models that continuously evolve over time, such as Very Fast Decision Trees (VFDT). However, it is not natural to use decision trees when learning has to be continuous --- which it frequently does due to concept drift --- because it is costly to adjust the tree's shape with new data. We thus propose two efficient incremental learning algorithms based on neural networks, Sliding Mini-batch Neural Networks and Sliding Ensemble Neural Networks, which avoid this problem. The results of our experiment on the Dodgers Loop Sensor Dataset indicate that the performances of our algorithms converge to that of popular batch learners.

@@

		Because data instances in a data stream are usually dependent, it is natural to assume that the data instances in a sliding window are correlated to those in the previous sliding window.  Due to the dependency of data instances between different sliding windows, we concluded that it would be inefficient to build a neural network on each sliding window independently.

		We further improved the model by choosing to pass the weights from one neural network to the subsequent neural network only in the case where there is no concept drift in the dataset. Moreover, by doing so, the training time gets reduced, since passing weights provides ``good weights'' as  initialization weights for each new neural network model.

>>>>

		\begin{abstract}
			%\boldmath

			Learning from data streams is a research area of increasing importance \cite{evaluation_stream_mining}. Nowadays, several stream mining algorithms have been developed. Most of them learn decision tree models that continuously evolve over time, such as Very Fast Decision Trees (VFDT). However, it is not natural to use decision trees when learning has to be continuous --- which it frequently does due to concept drift --- because it is costly to adjust the tree's shape with new data. We thus propose two efficient incremental learning algorithms based on neural networks, Sliding Mini-batch Neural Networks and Sliding Ensemble Neural Networks, which avoid this problem. The results of our experiment on the Dodgers Loop Sensor Dataset indicate that the performances of our algorithms converge to that of popular batch learners.

@@

		Because data instances in a data stream are usually dependent, it is natural to assume that the data instances in a sliding window are correlated to those in the previous sliding window.  Due to the dependency of data instances between different sliding windows, it would be inefficient to build a neural network on each sliding window independently.

		We further improved the model by choosing to pass the weights from one neural network to the subsequent neural network only in the case where there is no concept drift in the dataset. Moreover, by doing so, the training time gets reduced, since passing weights provides ``good weights'' as  initial weights for each new neural network model.
